---
output:
    github_document:
        df_print: kable
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bmgarch

`bmgarch` estimates Bayesian multivariate generalized autoregressive conditional heteroskedasticity (MGARCH) models.
Currently, bmgarch supports ARMA(1,1) and intercept-only (Constant) mean structures, and a variety of MGARCH(P,Q) parameterizations.
In increasing order of complexity:

* CCC(P, Q): Constant Conditional Correlation
* DCC(P, Q): Dynamic Conditional Correlation
* BEKK(P, Q): Baba, Engle, Kraft, and Kroner
* pdBEKK(P, Q): BEKK(P, Q) with positive diagonal constraints

## Installation

`bmgarch` is not yet available on CRAN.

The development version can be installed from [GitHub](https://github.com/) with:

``` r
devtools::install_github("ph-rast/bmgarch")
```
## Example

In this example, we use the pdBEKK(1,1) model for the variances, and an intercept-only model for the means.

```{r example}
library(bmgarch)

data(panas)
head(panas)

# Fit pdBEKK(1, 1) with ARMA(1,1) on the mean structure.
fit <- bmgarch(panas,
               parameterization = "pdBEKK",
               iterations = 1000,
               P = 1, Q = 1,
               distribution = "Student_t",
               meanstructure = "constant")

```

### Parameter estimates
```{r}
summary(fit)
```

### Forecasted values
```{r}
fit.fc <- forecast(fit, ahead = 5)

fit.fc
```

```{r forecastPlot}
plot(fit.fc, askNewPage = FALSE, type = "var")

plot(fit.fc, askNewPage = FALSE, type = "cor")
```
